%-----------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,10pt]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip}
\usepackage{fancyhdr}

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage[scale=0.92]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{8pt}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0,0}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
        \textbf{#1} & \hfill & {\footnotesize #2} \\[0.5pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill & {\footnotesize #2} \\[0.5pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=1pt,label=$\circ$]
    }
    {
    \end{itemize}
    \end{minipage}    
    }

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

\begin{tabularx}{\linewidth}{@{} C @{}}
    \Huge{Elia Franzella --- Software Developer} \\[7.5pt]
    \href{https://github.com/nin93}{\raisebox{-0.05\height}\faGithub\ nin93} \ $|$ \ 
    \href{https://www.linkedin.com/in/elia-franzella-20a046234/}{\raisebox{-0.05\height}\faLinkedin\ elia-franzella} \ $|$ \ 
    \href{https://www.franzella.dev}{\raisebox{-0.05\height}\faGlobe \ franzella.dev} \ $|$ \ 
    \href{mailto:franzella.elia@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ franzella.elia@gmail.com} \ $|$ \ 
    \href{tel:+393273469715}{\raisebox{-0.05\height}\faMobile \ +39 3273469715}  \ $|$ \ 
    \raisebox{-0.05\height}\faMapMarker \ Palermo, Italy \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%   SUMMARY
%----------------------------------------------------------------------------------------

\section{Summary / Objective}
Software developer with 5 years of experience designing and implementing scalable, cloud-native and event-driven backend systems. I have collaborated closely with product managers, designers and DevOps teams in large, product-focused organizations, working within Agile/Scrum cycles and rapid integration and delivery workflows. I am now seeking a role where I can leverage my full-stack development skills in challenging and innovative projects.

%----------------------------------------------------------------------------------------
%   WORK HISTORY
%----------------------------------------------------------------------------------------

\section{Work History}

\begin{joblong}{Backend Developer -- GIGLIO.COM S.p.A.}{Jan 2022 / Jan 2026 -- Palermo, Italy}
    \item Redesigned the e-commerce catalog ranking system from scratch, incorporating asynchronous and incremental updates with BullMQ and MongoDB, cutting rank synchronization times by 90\% in the worst-case scenarios.
    \item Developed a cross-platform routing and origin-tracking server, allowing the launch of the e-commerce mobile app and the centralization of web resources.
    \item Integrated Atlas Search’s semantic search into the e-commerce platform, boosting search performance by 15\% and improving both user experience and results availability.
    \item Optimized several APIs using advanced caching patterns backed by Redis, reducing retrieval times by 70\% on average while retaining data freshness.
    \item Rescued -- and extended with custom Bash scripts -- a legacy Linux CUPS printing system, using Nmap and ARP utilities to inspect and audit networks.
\end{joblong}

\vspace{-8pt}
Proficiencies: {\footnotesize \textbf{TypeScript}, \textbf{JavaScript}, \textbf{NestJS}, \textbf{MySQL}, \textbf{MongoDB}, \textbf{Redis}, \textbf{GraphQL}, \textbf{REST}, \textbf{gRPC}, \textbf{GNU/Linux}, \textbf{Docker}, \textbf{Git}.}

\begin{jobshort}{Junior Backend Developer -- Manpower S.r.l.}{Mar 2021 / Jan 2022 -- Palermo, Italy}
Development of modern, technical backend solutions within the microservice-based software ecosystems of clients.
\end{jobshort}
  
%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
    Languages: & {\footnotesize \textbf{TypeScript/JavaScript} (Node.js), \textbf{Rust}, \textbf{Python}, \textbf{C/C++}, \textbf{Bash}, \textbf{HTML5}, \textbf{CSS3}} \\
    Frameworks, libraries: & {\footnotesize \textbf{NestJS} (microservices), \textbf{React}, \textbf{Next.js}, \textbf{Qwik}, \textbf{TailwindCSS}, \textbf{Jest} (unit, end-to-end testing)} \\
    Infrastructure: & {\footnotesize \textbf{Docker}, \textbf{GNU/Linux}, \textbf{RabbitMQ}, \textbf{BullMQ}} \\
    Databases: & {\footnotesize \textbf{MySQL}, \textbf{PostgreSQL}, \textbf{MongoDB}, \textbf{Redis}} \\
    API design: & {\footnotesize \textbf{REST}, \textbf{gRPC}, \textbf{GraphQL}, \textbf{SOAP}} \\
    Methodologies: & {\footnotesize \textbf{Agile}, \textbf{Scrum}, \textbf{CI/CD}} \\
    Version control: & {\footnotesize \textbf{Git}} \\
\end{tabularx}

\begin{tabularx}{\linewidth}{@{}l X@{}}
    \textbf{Analytical quick thinking}: Ability to promptly identify incident culprits and provide mitigation and fulfilling solutions. \\
    \textbf{Autonomy and self-learning}: Mastery of new technologies through self-initiative to solve real problems. \\
    \textbf{Time management}: Efficient task dispatching and priority self-management without in-team deadlocks. \\
    \textbf{Adaptability}: Flexibility and managing change in fast-paced, dynamic and high-demanding environments. \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%   PROJECTS
%----------------------------------------------------------------------------------------

\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
    \textbf{stateofneptune.com} & \hfill \href{https://www.stateofneptune.com}{\footnotesize Link to Demo } \\[0pt]
    \multicolumn{2}{@{}X@{}}{State Of Neptune’s official band website. Single page application built with the Qwik framework and styled using TailwindCSS.}  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
    \textbf{Alea} & \hfill \href{https://github.com/nin93/alea}{\footnotesize Link to Code } \\[0pt]
    \multicolumn{2}{@{}X@{}}{Utility library to work with most known probability distributions. Features pseudo-random number generator (PRNG) implementations, high-level APIs for repeatable random sampling and cumulative distribution functions (CDF) computing.}  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
    \textbf{Talgene} & \hfill \href{https://github.com/nin93/talgene}{\footnotesize Link to Code } \\[0pt]
    \multicolumn{2}{@{}X@{}}{Abstraction layer over genetic algorithm implementations featuring auto-iterations over generation advances and built-in genetic cross functions.}  \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
    (discontinued) & Physics Bachelor’s Degree at \textbf{University of Palermo} \hfill \footnotesize Palermo, Italy \\ 
    & High School Diploma at \textbf{Scientific high school B. Croce} \hfill \footnotesize Palermo, Italy \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%  LANGUAGES
%----------------------------------------------------------------------------------------

\section{Languages}
\begin{tabularx}{\linewidth}{@{}l X@{}}
    \textbf{Upper Intermediate English} (B2) & \hfill \footnotesize Academic Language Center - University of Palermo \\
    \textbf{Italian Native Speaker} (C1)
\end{tabularx}

%----------------------------------------------------------------------------------------
%	FOOTER
%----------------------------------------------------------------------------------------

\fancypagestyle{plain}{%
\fancyhf{} % clear all header and footer fields
\fancyfoot[C]{
     \scriptsize \textit{I hereby authorize the processing of my personal data in accordance with EU Regulation 2016/679 (GDPR) for the purpose of recruitment and selection}
}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}}

\pagestyle{plain}

\end{document}
